---
title: "Part 1 Multiple Linear Regression"
author: "Roshni Katrak-Adefowora"
date: "12/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(stargazer)
```

## Visual exploration

```{r}
penguins %>% 
  ggpairs() #entire matrix of all possible relationships and distribution within each variable

#lets just look at continuous variables
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color=species)) #colors based on species

#looks like there are linear relationship and not super high correlations that would suggest multicollinearity --> multilinear regression is good to go!
```

## Build a few different models

The 4 model versions we will compare for this exercise are: 

(1) Penguin Mass ~ Flipper Length + Species
(2) Penguin Mass ~ Flipper Length + Species
(3) Penguin Mass ~ Flipper Length + Species + Sex + Bill Length
(4) Penguin Mass ~ Flipper Length + Species + Sex + Bill Length + Island


```{r}
lm1 <- lm(body_mass_g ~ flipper_length_mm + species, data=penguins)

lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data=penguins)

lm3 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm, data=penguins)

lm4 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm + island, data=penguins)
```

## Find AIC value for each model

Absolute value of AIC model doesn't mean anything. It's relative.
```{r}
AIC(lm1)
AIC(lm2) #lower, good add of complexity
AIC(lm3) #even lower
AIC(lm4) #goes back up, the addition of island (added complexity) was not worth the increase in model fit

#based on AIC, lm3 is lowest--> has the best balance of model fit and model complexity
```

## Use stargazer package for a table with multiple model outputs

```{r, results = "asis"}
stargazer(lm1, lm3, lm4, type="html")
```

## Omitted variable bias

```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=bill_depth_mm))+
  geom_point()+
  geom_smooth(method="lm") #looks like there's an overall negative relationship between flipper length and bill depth. BUT!!! Is species important?
```
```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=bill_depth_mm, group=species))+
  geom_point(aes(color=species))+
  geom_smooth(method="lm") #applied within each species because of the grouping above
#Now we see a positive relationship!
#example of Simpson's paradox
```

